%LTeX: language=en-US

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
  \textbf{\Huge \scshape Andres Vasquez-Restrepo} \\ \vspace{1pt}
  \small (+57)3005258250 $|$ \href{mailto:anvasquezre@gmail.com}{\underline{anvasquezre@gmail.com}} $|$
  \href{https://linkedin.com/in/anvasquezre}{\underline{linkedin.com/in/anvasquezre}} $|$
  \href{https://github.com/anvasquezre}{\underline{github.com/anvasquezre}} $|$ Medellin, Colombia

\end{center}

\paragraph{}
Senior Machine Learning Engineer with over five years (5+) of experience specializing
in NLP, Document AI, speech analytics, and unstructured data analysis. I have
designed and deployed more than 8 AI solutions in production, optimizing
pipelines that process thousands of requests per hour and hundreds of documents
and audio hours with 95\% accuracy. My expertise spans PyTorch, OpenCV, YOLO,
and LangChain, with a strong focus on MLOps to ensure scalable, reliable AI
systems.

\paragraph{}I have led projects that analyze large-scale text and speech data, enabling
75\% faster decision-making and automating hundreds of hours of manual work per
week. I thrive on bridging the gap between AI research and business impact,
translating complex models into real-world solutions that drive measurable
results.

Beyond coding, I enjoy simplifying technical concepts for engineers, business
teams, and clients—because clear communication is as vital as well-optimized
algorithms.


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Master of Science in Artificial Intelligence }{La Rioja, España}
{Universidad Internacional de la Rioja}{Sept. 2024 -- Present}
\resumeSubheading
{Master of Science in Computational Biology and Bioinformatics }{Medellín, Colombia}
{Universidad Nacional de Colombia}{Aug. 2019 -- Dec. 2021}

\resumeSubheading
{Bachelor of Engineering in Biotechnology}{Medellín, Colombia}
{Universidad Nacional de Colombia}{Jan. 2014 -- Aug . 2019}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Senior Machine Learning Engineer (L4)}{Aug. 2024 -- Present}
{Provectus}{SF, USA, Remote}
\resumeItemListStart
\resumeItem{Led the development of machine learning workflows for data processing, model training, evaluation, and deployment in “The Sphere” project.}
\resumeItem{Took ownership of critical ML tasks and features, ensuring integration, optimization, and alignment with project goals.}
\resumeItem{Implemented MLOps best practices, including data and model versioning, experiment tracking, and reproducibility for large-scale LLM deployments.}
\resumeItem{Developed and optimized distributed training pipelines using multi-GPU/TPU architectures for large-scale NLP models.}
\resumeItem{Designed and deployed cloud-native ML solutions on AWS, leveraging serverless architectures, cost optimization strategies, and multi-cloud integrations.}
\resumeItem{Integrated large-scale text data pipelines with cloud-based data lakes and warehouses, ensuring efficient storage, retrieval, and processing.}
\resumeItem{Collaborated with cross-functional teams to align ML models with business objectives, ensuring high-impact AI solutions.}
\resumeItemListEnd


\resumeSubheading
{Lead Machine Learning and Artificial Intelligence Engineer}{Jul. 2023 -- Aug. 2024}
{Tenant Evaluation}{FL, USA, Remote}
\resumeItemListStart
\resumeItem{Designed, developed, and deployed over 5 AI/ML solutions while mentoring junior developers.}
\resumeItem{Engineered a production-grade AI-driven virtual assistant serving 20,000 users monthly, reducing support ticket load by 50\%.}
\resumeItem{Architected a microservices framework with 6 components integrating REST APIs and WebSockets.}
\resumeItem{Implemented a Document AI platform automating 75\% of internal document processing, cutting costs from \$9,000 to \$236 per month.}
\resumeItemListEnd

\resumeSubheading
{Machine Learning Engineer}{Sep. 2022 -- Jul. 2023}
{AnyoneAI}{ SF, USA, Remote}
\resumeItemListStart
\resumeItem{Developed and deployed 3+ end-to-end ML solutions for global clients, covering recommendation systems and classification models.}
\resumeItem{Built and maintained ML models for NLP, Computer Vision, and Business Intelligence applications.}
\resumeItem{Automated e-commerce reporting with Apache Airflow, reducing report generation time from hours to minutes.}
\resumeItemListEnd

\resumeSubheading
{Data Scientist}{Sep. 2021 -- Sep. 2022}
{Grinsup}{Medellín, Colombia}
\resumeItemListStart
\resumeItem{Developed pricing algorithms that maintained a 40\% gross profit margin, boosting net profit by 10\%.}
\resumeItem{Created nutritional estimation models using multi-objective optimization for efficient product development.}
\resumeItem{Recognized as a leader in Colombian innovation and selected for the Young Leaders of the Americas initiative.}
\resumeItemListEnd

\resumeSubheading
{Data Analyst}{Sep. 2019 -- Sep. 2021}
{Centricol Industries}{Medellín, Colombia}
\resumeItemListStart
\resumeItem{Led market analysis to develop new biotechnology product lines, increasing revenue by 50\% in two years.}
\resumeItem{Improved data accessibility by 30\% through centralized data repository implementation.}
\resumeItem{Generated sales reports that enabled a 50\% increase in revenue through targeted product strategies.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{Job Recommendation System for Hunty}}{Mar 2023}
\resumeItemListStart
\resumeItem{Developed an end-to-end job recommendation API integrating daily web scraping using Ada-02 embeddings.}
\resumeItem{Implemented FastAPI with MongoDB and MariaDB for scalable data storage.}
\resumeItem{Automated job ingestion using DAGs in Apache Airflow, reducing manual work and improving efficiency.}
\resumeItem{Enabled the platform to post over 1,000 new jobs daily and rank them based on user profiles.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{ChatFLOW}}{Jan 2023}
\resumeItemListStart
\resumeItem{Developed an open-source, drag-and-drop chatbot design platform similar to Voiceflow.}
\resumeItem{Implemented state-of-the-art NLP techniques and Generative AI models to enhance user interactions.}
\resumeItem{Built modular components enabling users to craft detailed conversational flows with minimal coding.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
        \textbf{Programming Languages}{: Python, Javascript, Java} \\
        \textbf{Machine Learning}{: SQL, TensorFlow, Pytorch, Scikit-learn, XGBoost, LightGBM, LLM, SML, Finetunning, HuggingFace, LangChain, OpenCV, YOLO, Llama.cpp} \\
        \textbf{Data Processing}{: Pandas, NumPy, NLTK, OpenCV, NetworkX, Apache Airflow} \\
        \textbf{Cloud \& MLOps}{: AWS (EC2, EKS, Lambda, S3, SageMaker, CloudWatch, RDS, DocumentDB, SQS), Kubernetes, Docker, MLflow, ArgoCD, Jenkins, Rundeck, Grafana, Bash} \\
        \textbf{Web Frameworks}{: FastAPI, Django} \\
        \textbf{Databases}{: PostgreSQL, MongoDB, Redis} \\
        \textbf{Developer Tools}{: Git, Bitbucket, Jira}
        }}
\end{itemize}

%-----------CERTIFICATIONS-----------
\section{Certifications}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
        \textbf{AWS AI Practitioner}{: AWS} \\
        \textbf{English C1 Proficiency}{: Duolingo English Test 120/160} \\
        \textbf{Applied Machine Learning}{: University of Michigan} \\
        \textbf{Machine Learning with Python}{: IBM} \\
        \textbf{Leadership and Team management}{: University of Florida} \\
        \textbf{Leader of the Americas}{: Department of State, United States} \\

        }}
\end{itemize}

%-------------------------------------------
\end{document}

